\myTitle

### 2024-11-05 tex/body-text-of-paper.tex
Stuff

We include a marker that targets the sex-determining region ({\em sdY}) on the Y chromosome in Chinook salmon.
This marker characterizes genetic sex in Central Valley populations \comment{\citep{von2015development}}.
And, finally, we include marker Ots\_coho001\_05\_32691399 which is fixed for alternate alleles in
coho salmon and Chinook salmon.  This is helpful when samplers have unwitting
collected coho salmon from ocean catches.

>>>>

We include a novel marker that targets the sex-determining region ({\em sdY}) on the Y chromosome in Chinook salmon. We designed this marker through examination of whole-genome sequence data in multiple populations of California Chinook salmon (Thompson et al., 2020.)
This marker characterizes genetic sex in diverse California salmon populations more accurately than previously published marker assays \comment{\citep{von2015development}}.
And, finally, we include marker Ots\_coho001\_05\_32691399 which is fixed for alternate alleles in
coho salmon and Chinook salmon.  This is helpful when samplers have unwitting
collected coho salmon from ocean catches.
